### 2020-06-15 report/sections/background/interim/codegen.tex
Progress: start moving background

\section{Code Generation}
The EFSM describes the local session type and provides guidance to developers for verifying that their endpoint implementation conforms to the communication protocol. However, a direct encoding of the local session type into the target language of the implementation is usually not feasible as the EFSM assumes IO objects as first-class citizens and communication channels are linear resources, features that are left to be desired in mainstream programming languages (such as Java and Python) used by the developers' implementations. We note that languages with native session type support \cite{ATS2016} do exist, but their usage largely remains for research purposes as supposed to real-world application development.

>>>>

\section{Code Generation}
The EFSM describes the local session type and provides guidance to developers for verifying that their endpoint implementation conforms to the communication protocol. However, a direct encoding of the local session type into the target language of the implementation is usually not feasible as the EFSM assumes IO objects as first-class citizens and communication channels are linear resources, features that are left to be desired in mainstream programming languages (such as Java and Python) used by the developers' implementations. We note that languages with native session type support (e.g. ATS \cite{ATS2016}) exist, but their usage largely remains for research purposes as supposed to real-world application development.
